\mutagen: Coverage-Guided, Property-Based Testing using Exhaustive Type-Preserving Mutations

### 2021-04-07 papers/oopsla-21/main.tex
Added WebAssembly evaluation

However, the authors acknowledge that certain parts of its implementation have
room for improvement, especially when it comes to the mutators design.
%
In tandem with the lack of efficacy observed when replicating the evaluation of
the IFC stack machine case study, these observations led us to consider three
main aspects of \fuzzchick that can be improved upon --- and that constitute the
main goal of this work.
%
%% As mentioned earlier, when we recreated the evaluation of the IFC stack machine
%% case study (described in detail in Section \ref{sec:casestudies}), we found that
%% after 30 runs (as opposed to the 5 runs used original by
%% \citeauthor{lampropoulos2019coverage}), \emph{\fuzzchick was only able to find 5
%%   out of the 20 injected bugs with a failure rate of 1}, the hardest one being
%% found only around 13\% of the time after an hour of testing.
%% %
%% These results are presented in detail in Section \ref{sec:evaluation}.
%
%% At the light of these observations, we identified three main aspects of
%% \fuzzchick that can be improved upon --- and that constitute the main goal of
%% this work.
%
In no particular order:
%
\begin{itemize}
\item \emph{Mutators distribution:} if we inspect the mutator defined in Fig.
  \ref{fig:fuzzchick:mutator}, there are two compromises that the authors of
  \fuzzchick adopted for the sake of simplicity.
  %
  On one hand, deep recursive mutations are very unlikely, since their
  probability decreases multiplicatively with each recursive call.
  %
  For instance, mutating a subexpression that lies on the third level of a
  \texttt{Tree} happens with a probability smaller than $(1/6)^3 = \sim 0.0046$,
  and this only worsens as the type of the mutated value becomes more complex.
  %
  Hence, \fuzzchick mutators can only be effectively used to transform to
  shallow data structures, potentially excluding interesting applications that
  might require producing deeper valid values, e.g., programming languages,
  network protocols interactions, etc.
  %
  Ideally, mutations should be able to happen on every subexpression of the
  input seed in a reasonable basis.

@@

\item \emph{Enqueuing mutation candidates:} \fuzzchick uses two single queues for
  keeping valid and discarded mutation candidates.
  %
  Whenever a new test case is found interesting, it is placed \emph{at the end
    of its corresponding queue}.
  %
  If this test case happens to have discovered a whole new portion of the target
  code, it will not be further mutated until the rest of the queue ahead of it
  gets processed.
  %
  This can limit the effectiveness of the testing loop if the queues tend to
  grow more often than they tend to shrink, as interesting mutation candidates
  can get buried at the end of a long queue that only exercises the same portion
  of the target code.
  %
  In the extreme case, they might not processed at all within the testing budget.
  %
  Ideally, one would like a mechanism that prioritizes mutating test cases
  that discovers new portions of the code right away, and that is capable of
  jumping back and forth from mutation candidates whenever this happens.
  %
  We show in Section \ref{sec:heuristics} how this can be achieved by analyzing
  the execution information in order to prioritize test cases with novel
  execution traces.

\item \emph{Power schedule:} It is not clear how the power schedule used to
  assign energy to each mutable test case in \fuzzchick works in the context of
  high-level type-preserving mutations.
  %
  If it assigns too much energy to certain not-so-interesting seeds, some bugs
  might not be discovered in a timely basis.
  %
  Conversely, assigning too little energy to interesting test cases might cause
  that some bugs cannot be discovered at all unless the right mutation happens
  within the small available energy window --- randomly generating the same test
  case later on does not help, as it becomes uninteresting based on historic
  trace information.

  To keep the comparison fair, the authors replicated the same power schedule
  configuration used in AFL.
  %
  However, AFL uses a different mutation approach that works at the bit level.
  %
  This raises the question about what is the best power schedule configuration
  when using a high-level mutation approach --- something quite challenging to
  characterize in general given the expressivity of the data types used to
  drive the mutators.
\end{itemize}

@@

\begin{figure}[b]
\begin{multicols}{2}

@@

@@

In both case studies, we additionally show how the FIFO scheduling and trace
reset heuristics described in Section \ref{sec:heuristics} affect the testing
performance by disabling them when using our tool.
%
We call these variants \textit{no-FIFO} and \textit{no-reset}, respectively.
%
In the case of \textit{no-reset}, the amount of random mutations is no longer
controlled by this heuristic, so we fixed it to 25 random mutations throughout
the execution of the tool.

@@

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\vspace{-10pt}
\footnotesize
\begin{tabular}{ccccc}
\hline
\multicolumn{1}{c}{
  \multirow{2}{*}{Bug}} &
  \multicolumn{1}{c}{\multirow{2}{*}{\fuzzchick}} &
  \multicolumn{1}{c}{\multirow{2}{*}{\mutagen}} &
  \multicolumn{2}{c}{$A_{12}$ measure} \\
\cline{4-5}
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{Value} &
\multicolumn{1}{c}{Estimate} \\
\hline
1  & 13974.9 & 3632.7 & 0.89 & {\color{red} large} \\ \hline
2  & 23962.9 & 7122.3 & 0.90 & {\color{red} large} \\ \hline
3  & 19678.5 & 4633.9 & 0.89 & {\color{red} large} \\ \hline
4  & 20398.4 & 16831.2 & 0.72 & {\color{red} medium} \\ \hline
5  & 17348.1 & 2326.6 & 0.94 & {\color{red} large} \\ \hline
6  & 10727.1 & 2312.9 & 0.92 & {\color{red} large} \\ \hline
7  & 5070.7 & 332.9 & 0.91 & {\color{red} large} \\ \hline
8  & 5596.4 & 298.7 & 0.90 & {\color{red} large} \\ \hline
9  & 16402.4 & 26342.5 & 0.51 & negligible \\ \hline
10 & 11553.0 & 25044.5 & 0.55 & negligible \\ \hline
11 & 11304.3 & 2536.8 & 0.82 & {\color{red} large} \\ \hline
12 & 18507.3 & 14482.7 & 0.65 & {\color{red} small} \\ \hline
13 & 17961.5 & 13454.9 & 0.65 & {\color{red} small} \\ \hline
14 & 10621.9 & 3928.3 & 0.78 & {\color{red} large} \\ \hline
15 & 23866.3 & 43678.2 & 0.23 & {\color{blue} large} \\ \hline
16 & 25321.7  & 27602.0 & 0.54 & negligible \\ \hline
17 & 28515.6 & 52344.9 & 0.47 & negligible \\ \hline
18 & 24218.6 & 123401.3 & 0.14 & {\color{blue} large} \\ \hline
19 & 18638.9 & 30682.3 & 0.45 & negligible \\ \hline
20 & 18883.1 & 15841.9 & 0.60 & {\color{red} small} \\ \hline
& & Mean & 0.67 & {\color{red} medium} \\
\hline
\end{tabular}
\captionof{table}{\label{table:ifc:tests} Mean tests until first failure and effect size
  comparison between \fuzzchick and \mutagen when considering only succesfull
  runs.
  %
  Estimates in {\color{blue} blue} and {\color{red} red} indicate results
  favouring \fuzzchick and \mutagen, respectively. }
\vspace{-15pt}
\end{wrapfigure}

@@

Table \ref{table:ifc:tests} shows a comparison between the mean number of tests
required by both tools to find the first failure when we only consider
successful runs.
%
Additionally, as adviced by \cite{arcuri} when comparing random testing tools,
we computed the non-parametric Vargha-Delaney $A\_{12}$ measure \cite{vda}.
%
Intuitively, this measure encodes the probability of \mutagen to yield better
results than \fuzzchick.
%
As it can be observed, using an exhaustive mutation approach can be not only
more reliable, but also faster, where \mutagen is likely to find bugs faster
that \fuzzchick in 14 of the 20 bugs injected into the abstract machine.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{tikz/ifc-mttf.tikz}
  \includegraphics[width=\linewidth]{tikz/ifc-fr.tikz}
  \caption{\label{fig:results:ifc} Comparison between \fuzzchick and \mutagen
    across 20 different bugs for the IFC stack machine. }
\end{figure}

@@

On the other hand, disabling the trace saturation heuristic (\textit{no-reset})
we observed two interesting effects:
%
havig fixed the amount of random mutations to 25 adds a seemingly constant
overhead when finding most of the (easier) bugs, suggesting that we are spending
worthless time mutating numeric subexpressions inside the generated machine
states and that a smaller number of random mutations could be equally effective
to find such bugs.
%
However, some of the hardest to find bugs cannot be reliably exposed using this
amount of random mutations (\#4, \#9, \#12, \#18 and \#10), suggesting that one
should increase this number even further to be able to discover all bugs within
the time budget.
%
In consequence, we believe this heuristic is effective at automatically tunning
this internal parameter of our tool, especially when the user is unsure about
what the best value for it might be.

@@

Aliquam erat volutpat. Nunc eleifend leo vitae magna. In id erat non orci
commodo lobortis. Proin neque massa, cursus ut, gravida ut, lobortis eget,
lacus. Sed diam. Praesent fermentum tempor tellus. Nullam tempus. Mauris ac
felis vel velit tristique imperdiet. Donec at pede. Etiam vel neque nec dui
dignissim bibendum. Vivamus id enim. Phasellus neque orci, porta a, aliquet
quis, semper a, massa. Phasellus purus. Pellentesque tristique imperdiet tortor.
Nam euismod tellus id erat.

@@

@@

We presented \mutagen, a coverage-guided, property-based testing framework
written in Haskell.
%
Inspired by \fuzzchick, our tool uses coverage information to guide
automatically derived mutators producing high-level, type-preserving mutations.
%
However, instead of relying heavily on randomness and power schedules to find
bugs, our tool uses an exhaustive mutation approach that generates every
possible mutant for each interesting input candidate, and schedules it to be
tested exactly once.
%
This is in turn inspired by exhaustive bounded testing tools that focus on
testing every possible input value of the system under test --- a more generic
technique of limited applicability.

@@

In the future, we will investigate how to redefine our automatically synthesized
mutators in a stateful manner.
%
This way, it would be possible to apply mutations that preserve complex
properties of the generated data like well-scopedness and well-typedness simply
by construction, e.g., mutations that \emph{always} produce well-typed
subexpressions that refer only to identifiers in the current scope.
%
The main challenge will be to achieve this while keeping the testing process as
automatable as possible.

>>>>

However, the authors acknowledge that certain parts of its implementation have
room for improvement, especially when it comes to the mutators design.
%
In tandem with the lack of efficacy observed when replicating the evaluation of
the IFC stack machine case study, these observations led us to consider three
main aspects of \fuzzchick that can be improved upon --- and that constitute the
main goal of this work.
%
%% As mentioned earlier, when we recreated the evaluation of the IFC stack machine
%% case study (described in detail in Section \ref{sec:casestudies}), we found that
%% after 30 runs (as opposed to the 5 runs used original by
%% \citeauthor{lampropoulos2019coverage}), \emph{\fuzzchick was only able to find 5
%%   out of the 20 injected bugs with a failure rate of 1}, the hardest one being
%% found only around 13\% of the time after an hour of testing.
%% %
%% These results are presented in detail in Section \ref{sec:evaluation}.
%
%% At the light of these observations, we identified three main aspects of
%% \fuzzchick that can be improved upon --- and that constitute the main goal of
%% this work.
%
In no particular order:

\paragraph{Mutators distribution:}
%
if we inspect the mutator defined in Fig. \ref{fig:fuzzchick:mutator}, there are
two compromises that the authors of \fuzzchick adopted for the sake of
simplicity.
%
On one hand, deep recursive mutations are very unlikely, since their probability
decreases multiplicatively with each recursive call.
%
For instance, mutating a subexpression that lies on the third level of a
\texttt{Tree} happens with a probability smaller than $(1/6)^3 = \sim 0.0046$,
and this only worsens as the type of the mutated value becomes more complex.
%
Hence, \fuzzchick mutators can only be effectively used to transform to shallow
data structures, potentially excluding interesting applications that might
require producing deeper valid values, e.g., programming languages, network
protocols interactions, etc.
%
Ideally, mutations should be able to happen on every subexpression of the input
seed in a reasonable basis.

@@

\paragraph{Enqueuing mutation candidates:}
%
\fuzzchick uses two single queues for keeping valid and discarded mutation
candidates.
%
Whenever a new test case is found interesting, it is placed \emph{at the end of
  its corresponding queue}.
%
If this test case happens to have discovered a whole new portion of the target
code, it will not be further mutated until the rest of the queue ahead of it
gets processed.
%
This can limit the effectiveness of the testing loop if the queues tend to grow
more often than they tend to shrink, as interesting mutation candidates can get
buried at the end of a long queue that only exercises the same portion of the
target code.
%
In the extreme case, they might not processed at all within the testing budget.
%
Ideally, one would like a mechanism that prioritizes mutating test cases that
discovers new portions of the code right away, and that is capable of jumping
back and forth from mutation candidates whenever this happens.
%
We show in Section \ref{sec:heuristics} how this can be achieved by analyzing
the execution information in order to prioritize test cases with novel execution
traces.

\paragraph{Power schedule:}
%
It is not clear how the power schedule used to assign energy to each mutable
test case in \fuzzchick works in the context of high-level type-preserving
mutations.
%
If it assigns too much energy to certain not-so-interesting seeds, some bugs
might not be discovered in a timely basis.
%
Conversely, assigning too little energy to interesting test cases might cause
that some bugs cannot be discovered at all unless the right mutation happens
within the small available energy window --- randomly generating the same test
case later on does not help, as it becomes uninteresting based on historic trace
information.

To keep the comparison fair, the authors replicated the same power schedule
configuration used in AFL.
%
However, AFL uses a different mutation approach that works at the bit level.
%
This raises the question about what is the best power schedule configuration
when using a high-level mutation approach --- something quite challenging to
characterize in general given the expressivity of the data types used to drive
the mutators.\\

@@

@@

\begin{table}[t]
\footnotesize
\begin{tabular}{|c|c|l|}
\hline
\textbf{Id}
& \textbf{Subsystem}
& \textbf{Description} \\
\hline
1
& Validator
& Wrong if-then-else type validation on else branch \\
\hline
2
& Validator
& Wrong stack type validation \\
\hline
3
& Validator
& Removed function type mismatch assertion \\
\hline
4
& Validator
& Removed max memory instances assertion \\
\hline
5
& Validator
& Removed function index out-of-range assertion \\
\hline
6
& Validator
& Wrong type validation on \texttt{i64.eqz} instruction \\
\hline
7
& Validator
& Wrong type validation on \texttt{i32} binary opertations \\
\hline
8
& Validator
& Removed memory index out-of-range assertion \\
\hline
9
& Validator
& Wrong type validation on \texttt{i64} constants \\
\hline
10
& Validator
& Removed memory alignment validation on \texttt{i32.load} instruction \\
\hline
11
& Interpreter
& Wrong intepretation of \texttt{i32.sub} instruction \\
\hline
12
& Interpreter
& Wrong intepretation of \texttt{i32.lt\_u} instruction when operands are equal \\
\hline
13
& Interpreter
& Wrong intepretation of \texttt{i32.shr\_u} instruction \\
\hline
14
& Interpreter
& Wrong local variable initialization \\
\hline
15
& Interpreter
& Wrong memory address casting on \texttt{i32.load8\_s} instruction \\
\hline
\end{tabular}
\caption{\label{table:wasm:injectedbugs}Bugs injected in \textit{haskell-wasm}.}
\end{table}

@@

In both case studies, we additionally show how the FIFO scheduling and trace
reset heuristics described in Section \ref{sec:heuristics} affect the testing
performance by disabling them when using our tool.
%
We call these variants \textit{no FIFO} and \textit{no reset}, respectively.
%
In the case of \textit{no reset}, the amount of random mutations is no longer
controlled by this heuristic, so we fixed it to 25 random mutations throughout
the execution of the tool.

@@

\begin{figure}[b]
  \centering
  \includegraphics[width=\linewidth]{tikz/ifc-mttf.tikz}
  \includegraphics[width=\linewidth]{tikz/ifc-fr.tikz}
  \caption{\label{fig:results:ifc} Comparison between \fuzzchick and \mutagen
    across 20 different bugs for the IFC stack machine. }
\end{figure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\vspace{-20pt}
\footnotesize
\begin{tabular}{ccccc}
\hline
\multicolumn{1}{c}{
  \multirow{2}{*}{Bug}} &
  \multicolumn{1}{c}{\multirow{2}{*}{\fuzzchick}} &
  \multicolumn{1}{c}{\multirow{2}{*}{\mutagen}} &
  \multicolumn{2}{c}{$A_{12}$ measure} \\
\cline{4-5}
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{} &
\multicolumn{1}{c}{Value} &
\multicolumn{1}{c}{Estimate} \\
\hline
1  & 13974.9 & 3632.7 & 0.89 & {\color{red} large} \\ \hline
2  & 23962.9 & 7122.3 & 0.90 & {\color{red} large} \\ \hline
3  & 19678.5 & 4633.9 & 0.89 & {\color{red} large} \\ \hline
4  & 20398.4 & 16831.2 & 0.72 & {\color{red} medium} \\ \hline
5  & 17348.1 & 2326.6 & 0.94 & {\color{red} large} \\ \hline
6  & 10727.1 & 2312.9 & 0.92 & {\color{red} large} \\ \hline
7  & 5070.7 & 332.9 & 0.91 & {\color{red} large} \\ \hline
8  & 5596.4 & 298.7 & 0.90 & {\color{red} large} \\ \hline
9  & 16402.4 & 26342.5 & 0.51 & negligible \\ \hline
10 & 11553.0 & 25044.5 & 0.55 & negligible \\ \hline
11 & 11304.3 & 2536.8 & 0.82 & {\color{red} large} \\ \hline
12 & 18507.3 & 14482.7 & 0.65 & {\color{red} small} \\ \hline
13 & 17961.5 & 13454.9 & 0.65 & {\color{red} small} \\ \hline
14 & 10621.9 & 3928.3 & 0.78 & {\color{red} large} \\ \hline
15 & 23866.3 & 43678.2 & 0.23 & {\color{blue} large} \\ \hline
16 & 25321.7  & 27602.0 & 0.54 & negligible \\ \hline
17 & 28515.6 & 52344.9 & 0.47 & negligible \\ \hline
18 & 24218.6 & 123401.3 & 0.14 & {\color{blue} large} \\ \hline
19 & 18638.9 & 30682.3 & 0.45 & negligible \\ \hline
20 & 18883.1 & 15841.9 & 0.60 & {\color{red} small} \\ \hline
& & Mean & 0.67 & {\color{red} medium} \\
\hline
\end{tabular}
\captionof{table}{\label{table:ifc:tests} Mean tests until first failure and effect size
  comparison between \fuzzchick and \mutagen when considering only succesfull
  runs.
  %
  Estimates in {\color{blue} blue} and {\color{red} red} indicate results
  favouring \fuzzchick and \mutagen, respectively. }
\vspace{-25pt}
\end{wrapfigure}

@@

Table \ref{table:ifc:tests} shows a comparison between the mean number of tests
required by both tools to find the first failure when we only consider
successful runs.
%
Additionally, as adviced by \cite{arcuri} when comparing random testing tools,
we computed the non-parametric Vargha-Delaney $A_{12}$ measure \cite{vda}.
%
Intuitively, this measure encodes the probability of \mutagen to yield better
results than \fuzzchick.
%
As it can be observed, using an exhaustive mutation approach can be not only
more reliable, but also faster, where \mutagen is likely to find bugs faster
that \fuzzchick in 14 of the 20 bugs injected into the abstract machine.

@@

On the other hand, disabling the trace saturation heuristic (\textit{no reset})
we observed two interesting effects:
%
havig fixed the amount of random mutations to 25 adds a seemingly constant
overhead when finding most of the (easier) bugs, suggesting that we are spending
worthless time mutating numeric subexpressions inside the generated machine
states and that a smaller number of random mutations could be equally effective
to find such bugs.
%
However, some of the hardest to find bugs cannot be reliably exposed using this
amount of random mutations (\#4, \#9, \#12, \#18 and \#10), suggesting that one
should increase this number even further to be able to discover all bugs within
the time budget.
%
In consequence, we believe this heuristic is effective at automatically tunning
this internal parameter of our tool, especially when the user is unsure about
what the best value for it might be.

@@

The results of this case study are shown in Fig. \ref{fig:results:wasm}, ordered
by the mean-time-to-failure achieved by \mutagen.
%
Given that we used different properties to test the WebAssembly validator and
interpreter, we will focus on these results independently.

Firstly, we focus on the bugs injected in the validator (Fig.
\ref{fig:results:wasm} left).
%
There, we can quickly conclude that \quickcheck is well suited to find most of
the bugs --- it merely finds a counterexample for the easier bugs \#4 and \#5 in
just 1 out of 30 runs!
%
The reason behind this simple: WebAssembly modules comprise several different
interconnected components, e.g., types and functions definitions, memory blocks,
imports, exports, etc.
%
All these components need to be valid and agree with each other in order for the
module to be correctly validated (modulo the injected bugs).
%
Using an automatically derived generator that generates each one of these
components independently is virtually unable to produce valid WebAssembly
modules.
%
Using the same random generator, however, \mutagen is able to consistently find
every bug in less than 20 seconds in the absolute worst case.

In terms of the heuristics implemented in our tool, we can observe two clear
phenomena.
%
On one hand, disabling the FIFO schedulng (case \textit{no FIFO}), the
hardest-to-find bugs (\#7, \#8 and \#1) are no longer found on every run.
%
Moreover, although bugs \#2, \#9, \#8 and \#6 are found with \%100 success rate
across runs, it takes several times longer for \mutagen to find them.
%
On the other hand, disabling the the trace saturation heuristic (case \textit{no
  reset}) and using a fixed number of 25 random mutation does not affect the
effectiveness of our tool, apart from adding again a mostly constant overhead on
the time required to find every bug --- suggesting that the value we arbitrarily
chose for this parameter is too large and should be left to be handled
automatically by our tool.

If we now pay attention to the bugs injected into the interpreter (Fig.
\ref{fig:results:wasm} right), we notice that finding bugs requires
substantially more time (minutes instead of seconds), since both interpreters
need to validate and run the inputs before producing a result to compare.
%
Perhaps more interestingly, we can observe a significant improvement on the
performance of \quickcheck in terms of failure rate.
%
This is of no surprise: we deliberately reduced the search space by using a
module stub when defining \texttt{prop\_interpreter} in our test suite.
%
Nonetheless, \mutagen still outperforms \quickcheck both in terms of failure
rate and mean time to failure.
%
Moreover, by disabling the FIFO scheduling we observe that the performance of
our tool gets more unstable, where the bugs \#12 and \#11 take substantially
less time to be found, whereas the bugs \#15 and \#14 cannot be found on every
run.
%
Finding where the best tradeoff lies in cases where the heuristics cause mixed
results like this is an interesting direction to aim future work.

@@

Finally, this case study gives us the opportunity to analyze the overhead
introduced by the code instrumentation and internal processing used in \mutagen
versus the stateless black-box approach of \quickcheck.
%
Table \ref{table:wasm:overhead} compares the total number of executed and passed
test per second that we obtained using each tool.
%
It is easy to conclude that \mutagen executes tests several times slower than
\quickcheck -- roughly 16x and 70x slower when testing \textit{prop\_validator}
and \textit{prop\_interpreter\_i32}, respectively.
%
Part of the reason behind this slowdown is that the code instrumentation our
tool currently uses is built upon a superficial tranformation that logs traces
at the user level.
%
We anticipate that a large portion of the overhead could be reduced considerably
by integrating the instrumentation directly into the Haskell runtime --- a
substantial challenge to tackle in the future.

More importantly, in the same time, our tool is capable of running many more
tests that pass the sparse preconditions than \quickcheck, and which ultimately
lead us to finding bugs.

\begin{table}[H]
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{
  \multirow{2}{*}{Property}}
  & \multicolumn{2}{c|}{\quickcheck}
  & \multicolumn{2}{c|}{\mutagen} \\
  \cline{2-5}
  \multicolumn{1}{|c|}{}
  & \multicolumn{1}{c|}{total}
  & passed
  & \multicolumn{1}{c|}{total}
  & passed \\
\hline
\textit{prop\_validator}
& 42136
& 0.00028
& 2583
& 539.19 \\
\hline
\textit{prop\_interpreter\_i32}
& 134000
& 23.16
& 1890
& 372.75 \\
\hline
\end{tabular}
\caption{\label{table:wasm:overhead}Mean number of tests per second executed by
  each tool on the WebAssembly case study.}
\end{table}

@@

We presented \mutagen, a coverage-guided, property-based testing framework
written in Haskell.
%
Inspired by \fuzzchick, our tool uses coverage information to guide
automatically derived mutators producing high-level, type-preserving mutations.
%
However, instead of relying heavily on randomness and power schedules to find
bugs, our tool uses an exhaustive mutation approach that generates every
possible mutant for each interesting input candidate, and schedules it to be
tested exactly once.
%
This is in turn inspired by exhaustive bounded testing tools that focus on
testing every possible input value of the system under test.

%% --- a more generic technique of limited applicability.

@@

As already indicated throughout this work, there are several direction for
future work we aim to investigate:
%
combining \mutagen with specialized generators; improving the code
instrumentation in order to effectively target mutations towards specific parts
of the code; and evaluating the effect of lazy prunning; among others.
%
In addition, we want to investigate how to redefine our automatically
synthesized mutators in a stateful manner.
%
This way, it would be possible to apply mutations that preserve complex
properties of the generated data simply by construction, e.g., mutations that
\emph{always} produce well-typed subexpressions that refer only to identifiers
in scope.
%
The main challenge will be to achieve this while keeping the testing process as
automatable as possible.
